Carbonate clumped isotope constraints on Silurian ocean temperature and $\delta^{18}$O

### 2013-08-19 draft.tex
moved flakes figure up to methods section and changed to color versions of figures
changed figure numbers to reflect new order, figure positions not perfect

@@

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{Fig_03_bw-01.png}
\caption{The $\delta^{13}$C, $\delta^{18}$O and clumped isotope temperature of all the samples analyzed in this study, plotted against stratigraphic height. For the Lower \& Upper Visby and H\"{o}gklint Formations, a height of zero meters is defined by the contact between the Lower Visby Beds and the Upper Visby Beds. For the Slite Formation, a height of zero meters is defined as an arbitrary bed near the base of the outcrop. Brachiopod $\delta^{13}$C and $\delta^{18}$O measurements from \cite{Munnecke2003} are also included. Error bars represent the standard error of the mean.}
\label{section}
\end{figure*}

@@

@@

\begin{figure*}[b]
\centering
\includegraphics[width=\textwidth]{Fig_05_bw-01.png}
\captionsetup{labelformat=empty} 
\caption{Figure 5: Scatter plots showing the relationship between temperature and bulk trace metal concentrations. The negative correlation between temperature and the log of Sr concentration in rugose corals is weakly significant (79\% confidence), and strengthens when combined with the rest of the samples. There are also weakly significant positive correlations between temperature and the log of Fe concentration (63\% confidence) and between temperature and the log of Mn concentration (83\% confidence) among all the samples combined. These plots demonstrate clear differences in trace metal content between the two fossil taxa and the later carbonate phases. Brachiopods have the lowest average temperature of all the sample subsets, and also tend to have the most pristine trace metal signatures, with less Fe and Mn and more Sr than the other samples. Micrites and cements have the highest average temperature and tend to have the most altered trace metal signatures, with high Fe and Mn and low Sr concentrations.}
\label{Brand}
\end{figure*}

\begin{figure}[t]
\centering
\includegraphics[width=90mm]{Fig_04_bw-01.png}
\captionsetup{labelformat=empty} 
\caption{Figure 4: Bulk manganese and strontium concentrations of the brachiopods, rugose corals, micrites and cements in this study. The brachiopods in this study have less Mn and more Sr than most of the brachiopods analyzed by \cite{Brand2012} which are also shown in this figure. Lines represent estimates by different authors of the range of pristine concentrations defined for brachiopods. Rugose corals generally have more Fe (not shown), more Mn and less Sr than brachiopods, giving them more altered trace metal signatures, while cements and micrites tend to have the most highly altered trace metal signatures. Figure modified from \cite{Brand2012}.}
\label{metals}
\end{figure}

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=140mm]{Fig_06_bw-01.png}
\caption{Calcite fabric and trace metal concentrations in a rugose coral. The four images show the same area of a rugose coral thin section, all at the same magnification. The black bar at the bottom of panel B is 500 $\mu$m long for scale. A) Transmitted light. The dark triangle labeled ``RC'' was identified as a recrystallized domain of the coral septum. Cement in the void space between coral septa appears as blocky calcite crystals. B) Electron backscatter diffraction (EBSD) analysis. The orientation of calcite crystals is indicated by different shades. The recrystallized domain is clearly marked by many calcite crystals with the same orientation. C) Iron and D) manganese concentrations measured using the E-probe. The maps are qualitative, with darker shades representing higher concentrations. For both metals, the recrystallized domain is indistinguishable from the rest of the septum. The black lines show the location of an array of 62 spots where trace metal concentrations were measured quantitatively. The concentration of Fe and Mn at these spots is plotted to the right of the respective map.}
\label{EBSD_coral}
\end{figure*}

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=\textwidth]{Fig_07_bw-01.png}
\caption{Calcite fabric in a brachiopod. A) Transmitted polarized light image of a thin section of brachiopod G3 LVF B1. This sample has a clumped isotope temperature of 35$^{\circ}$C. The boxed overlay is an electron backscatter diffraction (EBSD) image of the same sample. The orientation of calcite crystals is indicated by different shades. B) Euler pole figure generated from the EBSD analysis. The central band represents the preferential orientation of calcite crystals parallel to the outer surface of the brachiopod shell.}
\label{EBSD_brach}
\end{figure*}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{Fig_08-01.png}
\caption{Scanning electron microscope images of flakes of brachiopod shell. Images were taken in secondary electron mode. Panels A--C show flakes that were judged to be pristine and are representative of the material used for analysis. Panel D shows a flake that was judged to be partially recrystallized and would not have been chosen for analysis. Clumped isotope temperatures of the samples for which representative flakes are shown are: A) 35 $\pm$ 2$^{\circ}$C; B) 33 $\pm$ 2$^{\circ}$C; C) 35 $\pm$ 1$^{\circ}$C.}
\label{flakes}
\end{figure}

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{Fig_03-01.png}
\caption{Scanning electron microscope images of flakes of brachiopod shell. Images were taken in secondary electron mode. Panels A--C show flakes that were judged to be pristine and are representative of the material used for analysis. Panel D shows a flake that was judged to be partially recrystallized and would not have been chosen for analysis. Clumped isotope temperatures of the samples for which representative flakes are shown are: A) 35 $\pm$ 2$^{\circ}$C; B) 33 $\pm$ 2$^{\circ}$C; C) 35 $\pm$ 1$^{\circ}$C.}
\label{flakes}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{Fig_04_color-01.png}
\caption{The $\delta^{13}$C, $\delta^{18}$O and clumped isotope temperature of all the samples analyzed in this study, plotted against stratigraphic height. For the Lower \& Upper Visby and H\"{o}gklint Formations, a height of zero meters is defined by the contact between the Lower Visby Beds and the Upper Visby Beds. For the Slite Formation, a height of zero meters is defined as an arbitrary bed near the base of the outcrop. Brachiopod $\delta^{13}$C and $\delta^{18}$O measurements from \cite{Munnecke2003} are also included. Error bars represent the standard error of the mean.}
\label{section}
\end{figure*}

@@

@@

\begin{figure*}[b]
\centering
\includegraphics[width=\textwidth]{Fig_06_color-01.png}
\captionsetup{labelformat=empty} 
\caption{Figure 6: Scatter plots showing the relationship between temperature and bulk trace metal concentrations. The negative correlation between temperature and the log of Sr concentration in rugose corals is weakly significant (79\% confidence), and strengthens when combined with the rest of the samples. There are also weakly significant positive correlations between temperature and the log of Fe concentration (63\% confidence) and between temperature and the log of Mn concentration (83\% confidence) among all the samples combined. These plots demonstrate clear differences in trace metal content between the two fossil taxa and the later carbonate phases. Brachiopods have the lowest average temperature of all the sample subsets, and also tend to have the most pristine trace metal signatures, with less Fe and Mn and more Sr than the other samples. Micrites and cements have the highest average temperature and tend to have the most altered trace metal signatures, with high Fe and Mn and low Sr concentrations.}
\label{Brand}
\end{figure*}

\begin{figure}[t]
\centering
\includegraphics[width=90mm]{Fig_05_color-01.png}
\captionsetup{labelformat=empty} 
\caption{Figure 5: Bulk manganese and strontium concentrations of the brachiopods, rugose corals, micrites and cements in this study. The brachiopods in this study have less Mn and more Sr than most of the brachiopods analyzed by \cite{Brand2012} which are also shown in this figure. Lines represent estimates by different authors of the range of pristine concentrations defined for brachiopods. Rugose corals generally have more Fe (not shown), more Mn and less Sr than brachiopods, giving them more altered trace metal signatures, while cements and micrites tend to have the most highly altered trace metal signatures. Figure modified from \cite{Brand2012}.}
\label{metals}
\end{figure}

@@

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=140mm]{Fig_07_color-01.png}
\caption{Calcite fabric and trace metal concentrations in a rugose coral. The four images show the same area of a rugose coral thin section, all at the same magnification. The black bar at the bottom of panel B is 500 $\mu$m long for scale. A) Transmitted light. The dark triangle labeled ``RC'' was identified as a recrystallized domain of the coral septum. Cement in the void space between coral septa appears as blocky calcite crystals. B) Electron backscatter diffraction (EBSD) analysis. The orientation of calcite crystals is indicated by different shades. The recrystallized domain is clearly marked by many calcite crystals with the same orientation. C) Iron and D) manganese concentrations measured using the E-probe. The maps are qualitative, with darker shades representing higher concentrations. For both metals, the recrystallized domain is indistinguishable from the rest of the septum. The black lines show the location of an array of 62 spots where trace metal concentrations were measured quantitatively. The concentration of Fe and Mn at these spots is plotted to the right of the respective map.}
\label{EBSD_coral}
\end{figure*}

@@

\begin{figure*}[tb]
\centering
\includegraphics[width=\textwidth]{Fig_08_color-01.png}
\caption{Calcite fabric in a brachiopod. A) Transmitted polarized light image of a thin section of brachiopod G3 LVF B1. This sample has a clumped isotope temperature of 35$^{\circ}$C. The boxed overlay is an electron backscatter diffraction (EBSD) image of the same sample. The orientation of calcite crystals is indicated by different shades. B) Euler pole figure generated from the EBSD analysis. The central band represents the preferential orientation of calcite crystals parallel to the outer surface of the brachiopod shell.}
\label{EBSD_brach}
\end{figure*}

@@
